Distributed Multi-Heuristic A* (HAMSTAR)

### 2014-12-11 paper.tex
adding the hamstar since it's never mentioned in the report
Conclusion + Abstract

\abstract{A* is a popular graph search algorithm used in many artificial intelligence applications. The original A* algorithm makes use of a single heuristic to prioritize exploration through a graph, but a variation on the algorithm known as multi-heuristic A* (MHA*) makes use of multiple heuristics to more quickly arrive at approximate solutions. For this project we implemented a distributed version of MHA*, with one process per heuristic. We show... [performance]}
%TODO: Highlight important results

@@

Our algorithm is based off of the sequential, round-robin SMHA* code presented in \cite{Aine14} (Figure \ref{fig:pseudocode}). Our parallelized code was written in C++ with inter-process communication accomplished using MPI. The work was distributed over one or more of the 16-core machines in the Apt cluster. We associate one heuristic with each process that we run. In the following sections, we may use the terms machine and process interchangeably, even though we also tried running multiple heuristics (one per process) on one multi-core computer. % TODO: Machine specs here? Or in the experimental setup section?

@@

% TODO: Apt? Machine specs?

@@

% TODO: Fill me in!

>>>>

\abstract{A* is a popular graph search algorithm used in many artificial intelligence applications. The original A* algorithm makes use of a single heuristic to prioritize exploration through a graph, but a variation on the algorithm known as multi-heuristic A* (MHA*) makes use of multiple heuristics to more quickly arrive at approximate solutions. For this project we implemented a distributed version of MHA*, with one process per heuristic. We compare the results of our distributed implementation to the original MHA* algorithm. In particular, we provide evidence that in domains where state expansion is expensive, such as when heuristic calculations are slow, our distributed approach may outperform MHA*.

@@

Our algorithm is based off of the sequential, round-robin SMHA* code presented in \cite{Aine14} (Figure \ref{fig:pseudocode}). Our parallelized code was written in C++ with inter-process communication accomplished using MPI. The work was distributed over one or more of the 16-core machines in the Apt cluster. We associate one heuristic with each process that we run. In the following sections, we may use the terms machine and process interchangeably, even though we also tried running multiple heuristics (one per process) on one multi-core computer.

@@

@@

In this paper we outlined the details of a distributed version of the SMHA* algorithm. We detailed the structure of the algorithm, and presented experimental results comparing the performance of the algorithm while varying a number of parameters. We also compared its performance to the original SMHA* algorithm. Although we found that in the specific domain we tested on (the sliding tile puzzle) our distributed variant did not outperform the original algorithm, we provided evidence that our algorithm could outperform SMHA* in domains where heuristics are difficult to calculate, or in general where state expansion is expensive.
% TODO: Fill me in!
